Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-13 hscc2017/paper.tex
work on text

By contrast, we leverage a very recent step-change in the scalability of
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  
The candidate programs are iteratively refined to eventually match the desired program specification.   
Program synthesizers implementing the 
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture are now
able to generate programs for highly non-trivial specifications with a very 
high degree of automation.  Modern synthesis engines combine automated testing, 
genetic algorithms, 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,DBLP:conf/lpar/DavidKL15}.

By applying a state-of-the-art synthesis engine we are now able to present a
tool that automatically \emph{generates} digital controllers for a given
continuous plant model that are correct by construction.  This approach
promises to reduce the cost and time of development of digital control
dramatically, and requires considerably less expertise than methodologies
driven by verification.  Specifically, we synthesize controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{stable}.  Due to the complexity of such systems, in this work we focus
on linear models with known configurations and perform parametric synthesis
of stabilizing digital controllers.

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  Given our primary interest in stability despite
digitization effects, we have modeled a digital equivalent of the plant by
evaluating the effects of the quantizers (A/D and D/A converters) as time
discretization elements with quantization noise.  The resulting closed-loop
system is a program loop that operates on bit-vectors encoded using
fixed-point arithmetic with finite word length (FWL).  The deterministic
effects of the FWL and quantization errors are incorporated into the model
as an additive uncertainty, which is taken into account during the
CEGIS-based synthesis of the control software for the plant.

@@

\item We automatically generate {\em correct-by-construction} digital
  controllers using inductive synthesis.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as the effects of quantizers and FWL.  In particular, we
  have found that a two-stage verification engine that continuously refines
  the precision of the fixed-point representation of the plant yields a
  speed-up of two orders of magnitude over a conventional one-stage
  verification engine.

@@

We cover preliminaries on plant discretization, the verification of
closed-loop control systems, and stability in
Section~\ref{sec:preliminaries}.  Our core contribution is in
Section~\ref{sec:synthesis}: we present our CEGIS-based algorithm for
generating stable controllers for a given plant model.  Our experimental
setup and experimental results are given in Section~\ref{sec:experiments},
and we discuss how we extend the state-of-the-art beyond the existing
literature in Section~\ref{sec:related}.

>>>>

By contrast, we leverage a very recent step-change in the automation and scalability of 
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  
The candidate programs are iteratively refined to eventually match the desired program specification.   
Program synthesizers implementing the 
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture are now
able to generate programs for highly non-trivial specifications with a very 
high degree of automation.  Modern synthesis engines combine automated testing, 
genetic algorithms, 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,DBLP:conf/lpar/DavidKL15}.

By combining and applying state-of-the-art synthesis engines we present a 
tool that automatically generates digital controllers for a given 
continuous plant model that are correct by construction.  
This approach presents a high degree of autonomy, 
promises to reduce the cost and time of development of digital control dramatically, 
and requires considerably less expertise than a-posteriori verification methodologies.   
Specifically, we synthesize stable,  
%controllers for hybrid closed-loop systems, i.e., 
software-implemented embedded controllers along with a model of a physical plant. 
%, that are \emph{stable}.  
Due to the complexity of such closed-loop systems, in this work we focus
on linear models with known configurations, and perform parametric synthesis
of stabilizing digital controllers (further closed-loop requirements are left to future work).

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  
Towards our goal of closed-loop stability, 
% despite digitization effects, 
we have modeled a digital equivalent of the continuous plant by evaluating the effects of the quantizers (A/D and D/A converters) and of time
discretization. 
% elements with quantization noise.  
We further account for uncertainties on the plant models. 
The resulting closed-loop system is a program loop that operates on bit-vectors encoded using
fixed-point arithmetic with finite word length (FWL). 
The effects of the both the FWL and quantization errors are incorporated into the model, 
%as an additive uncertainty, 
and are taken into account during the CEGIS-based synthesis of the control software for the plant.

@@

\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as the effects of quantizers and FWL.  In particular, we
  have found that a two-stage verification engine that continuously refines
  the precision of the fixed-point representation of the plant yields a
  speed-up of two orders of magnitude over a conventional one-stage
  verification engine.

@@

\textcolor{cyan}{[if space is needed, the next paragraph can be cut. ]}
We cover preliminaries on plant discretization, the verification of
closed-loop control systems, and stability in
Section~\ref{sec:preliminaries}.  Our core contribution is in
Section~\ref{sec:synthesis}: we present our CEGIS-based algorithm for
generating stable controllers for a given plant model.  Our experimental
setup and experimental results are given in Section~\ref{sec:experiments},
and we discuss how we extend the state-of-the-art beyond the existing
literature in Section~\ref{sec:related}.
